RJObject Paper

### 2014-06-23 Documents/Paper/ms.tex
Dragging equations
:= for assignment
Updated affiliations

A proposal
for an object involves transforming its parameters to $[0, 1]$ using $F$,
making the proposal in terms of $u$, and then transforming back.
Specifically, the proposal chooses
a new value $x_i'$ from the current value $x_i$ as follows:
\begin{eqnarray}
u_i &=& F(x_i; \alpha)\\
u_i' &=& \textnormal{mod}\left(u_i + \delta_u, 1\right)\\
x_i' &=& G(u_i'; \alpha).
\end{eqnarray}
where $\delta_u$ is drawn from a heavy-tailed distribution.

@@

@@

\section*{Acknowledgements}
This work is supported by a Marsden Fast-Start grant
from the Royal Society of New Zealand. I would like to thank the following
people for valuable conversations and inspiration:
Anna Pancoast (UCSB), David Hogg (NYU), Daniel Foreman-Mackey (NYU),
Courtney Donovan (Auckland), Tom Loredo (), Iain Murray (Edinburgh),
John Skilling (MaxEnt Data Consultants), and Daniela Huppenkothen ().

>>>>

A proposal
for an object involves transforming its parameters to $[0, 1]$ using $F$,
making the proposal in terms of $u$, and then transforming back.
Specifically, the proposal chooses
a new value $x_i'$ from the current value $x_i$ as follows:
\begin{eqnarray}
u_i &:=& F(x_i; \alpha)\\
u_i' &:=& \textnormal{mod}\left(u_i + \delta_u, 1\right)\\
x_i' &:=& G(u_i'; \alpha).
\end{eqnarray}
where $\delta_u$ is drawn from a heavy-tailed distribution.

@@

The ``dragging'' process works as follows, and must be carried out on
each object:
\begin{eqnarray}
u_i &:=& F(x_i; \alpha)\\
x_i' &:=& G(x_i; \alpha')
\end{eqnarray}

@@

\section*{Acknowledgements}
This work is supported by a Marsden Fast-Start grant
from the Royal Society of New Zealand. I would like to thank the following
people for valuable conversations and inspiration:
Anna Pancoast (UCSB), David Hogg (NYU), Daniel Foreman-Mackey (NYU),
Courtney Donovan (Auckland), Tom Loredo (Cornell), Iain Murray (Edinburgh),
John Skilling (MaxEnt Data Consultants), and Daniela Huppenkothen
(Amsterdam, NYU).
